Assessing exposure to Atlantic Basin tropical storms in United States counties

### 2016-07-18 writing/DraftExposurePaper/DraftExposurePaper.Rmd
Map wind exposure

wind_exposed %>%
        mutate(storm_id = gsub("-", " (", storm_id),
               storm_id = paste0(storm_id, ")")) %>%
        kable(col.names = c("Storm", "# of exposed counties"),
              caption = "Top 10 storms based on the number of counties exposed, using a metric of wind.")
```
#### Is our 3-day window for rian exposure reasonable?

>>>>

wind_exposed %>%
        mutate(storm_id = gsub("-", " (", storm_id),
               storm_id = paste0(storm_id, ")")) %>%
        kable(col.names = c("Storm", "# of exposed counties"),
              caption = "Top 10 storms based on the number of counties exposed, using a metric of wind.")
```

Here are plots of the top four storms based on number of counties exposed by wind:

```{r echo = FALSE, fig.width = 10, fig.height = 8}
top_wind_exposed <- function(storm_id){
        my_map <- map_wind_exposure(storm_id, wind_limit = 18)
        my_map <- map_tracks(storm = storm_id, plot_object = my_map, 
                             plot_points = FALSE) + 
                ggtitle(paste0(gsub("-", " (", storm_id), ")"))
}

n <- 4
wind_plots <- lapply(wind_exposed$storm_id[1:n], top_wind_exposed)
names(wind_plots) <- letters[1:n]
grid.arrange(wind_plots$a, wind_plots$b, wind_plots$c,
             wind_plots$d, ncol = 2)
```
#### Is our 3-day window for rian exposure reasonable?
